%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%


\begin{document}
\setlength{\footskip}{5pt}
%----------HEADING-----------------
\centering\textbf{\Large Alessandro Monticelli} \\
  \vspace{0.25in}
  \centering{\small{\faPhone} +39-340-053-1380 \quad
        \href{mailto:alessandro.monticelli@live.com}{\faEnvelope \underline{alessandro.monticelli@live.com}} \quad
        \href{https://www.linkedin.com/in/ale-mont}{{\faLinkedin} \underline{Alessandro Monticelli}} \quad
        \href{https://github.com/aleemont1}{{\faGithub} \underline{aleemont1}}}

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Researcher}{Cesena, Italy}
      {Department of Engineering and Computer Science - University of Bologna}{July 2025 - Current}
      \resumeItemListStart
        \resumeItem{Technologies used} {C++, LoRa\textsuperscript{\textcopyright}}
        \resumeItem{Description}
          {
            \begin{itemize}
              \item Designed a proprietary segmented-packet protocol over LoRa\textsuperscript{\textcopyright} for reliable point-to-point telemetry, enhancing payload capacity and transmission integrity for aerospace applications.
              \item Conducted experimental field tests on a sounding rocket, achieving 95\% packet reconstruction success at 500m with a throughput of 540 Byte/s.
              \item Authoring a research paper under the supervision of prof. Andrea Piroddi, for submission to IEEE, extending LoRa\textsuperscript{\textcopyright} to support segmented payloads with applications in multi-agent systems and point-to-point communication.
            \end{itemize}
          } 
      \resumeItemListEnd
    \resumeSubheading{Project Manager}{Forlì, Italy}{Aurora Rocketry Team - Unibo}{April 2024 -- Current}
    \resumeItemListStart
        \resumeItem{Technologies used} {C++, LoRa\textsuperscript{\textcopyright}, Python}
        \resumeItem{Description}
        {\begin{itemize}
          \item Leading the development of an ESP32-based flight computer for a student sounding rocket, managing a team of 7 developers.
          \item Oversaw telemetry system integration with a custom LoRa\textsuperscript{\textcopyright} protocol, ground station interface, and flight algorithms.
          \item System became the basis of my bachelor thesis, culminating in successful field validation during static tests and simulations.
        \end{itemize}}
    \resumeItemListEnd
    \resumeSubheading{Embedded Software Engineer Intern}{Cesena, Italy}{SPOT. Digital Made Simple}{February 2024 -- May 2024}
    \resumeItemListStart
        \resumeItem{Technologies used} {Python, .NET 8.0, NuGet}
        \resumeItem{Description}
        {\begin{itemize}
          \item Reverse-engineered RF module drivers for smart cinema seats, extracting low-level control commands.
          \item Designed and developed a simulator replicating the IoT system behavior, reducing integration testing time by 60\%.
          \item Contributed to the refactoring of the IoT platform backend (Python, .NET 8.0).
        \end{itemize}
        }
    \resumeItemListEnd
    \resumeSubheading{Software developer}{Bologna, Italy}{UBM - Unibo Motorsport Team}{October 2023 -- April 2024}
    \resumeItemListStart
        \resumeItem{Technologies used} {Python, Vue.js, MySQL}
        \resumeItem{Description}
        {\begin{itemize}
          \item Enhanced database connection pooling, improving connection stability and query performance.
          \item Optimized QR code scanning algorithms for product placement in warehouses, increasing detection reliability.
        \end{itemize} 
        }
    \resumeItemListEnd
\resumeSubHeadingListEnd

\begin{comment}    
    \resumeSubheading
      {Other Company}{Location}
      {Position}{From - To}
      \resumeItemListStart
        \resumeItem{Technology you worked with/on}
          {Description}
        \resumeItem{Other technology you worked with/on}
          {Description}
      \resumeItemListEnd

    \resumeSubheading
      {Research Position}{Location}
      {Position}{From - To}
      \resumeItemListStart
        \resumeItem{Technology you worked with/on}
          {Description}
        \resumeItem{Other technology you worked with/on}
          {Description}
      \resumeItemListEnd
\end{comment}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {"Alma Mater Studiorum" - University of Bologna}{Cesena (FC), Italy}
      {Bachelor of Science in Computer Science and Engineering}{September 2021 -- July 2025}
      \resumeItemListStart
          \resumeItem{Thesis}{"Development and Optimization of a Telemetry System for Rockets - Architecture and Data Transmission using LoRa\textsuperscript{\textcopyright}"}
          \resumeItem{Relevant Coursework}{Object-Oriented Programming (Java, C\#), High Performance Computing (OpenMP, Open MPI, CUDA, SIMD), 
          Embedded Systems and Internet of Things (Arduino, ESP32 (rtOS), Raspberry Pi), Systems Integration and Virtualization (Docker, Vagrant, Kubernetes, Active Directory), Telecommunication Networks}
      \resumeItemListEnd
    \resumeSubheading
      {I.T.T. "G. Giorgi"}{Brindisi (BR), Italy}
      {High School Diploma in ICT and Telecommunications}{September 2016 -- June 2021}
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\begin{comment}
\section{Languages}
    \resumeSubHeadingListStart
    \resumeItem
      {Italian}{Native speaker}
    \resumeItem
      {English}{Level C1}
  \resumeSubHeadingListEnd
\end{comment}

%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Programming}{: C++, C, Python, Java, C\# (.NET 8.0). }
    \hfill
    }
  \item{
    \textbf{Embedded Systems \& IoT}{: ESP32 (FreeRTOS), Arduino, Raspberry Pi, sensor fusion, RTOS task scheduling.}
    \hfill
    }
  \item{
    \textbf{Networking \& Protocols}{: LoRa\textsuperscript{\textcopyright} custom protocols, MQTT, HTTP, Active Directory, DNS/DHCP configuration}
  }
  \item{
    \textbf{High Performance Computing}{: OpenMP, OpenMPI, CUDA, SIMD}
  }
  \item{
    \textbf{Systems Integration}{: Docker, Kubernetes (basic), CI/CD pipelines with GitHub Actions}
  }
  \item{
    \textbf{Operating Systems}{: Linux (desktop \& server), Windows Server (AD, GPOs).}
      \hfill
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/aleemont1/OKINsimulator}{OKIN Simulator}}
      {Simulator of smart cinema seat control systems, replicating real-world device interactions with a modular architecture in Python.}
    \resumeSubItem{\href{https://github.com/aleemont1/esiot-23-24-assignment3/}{River Monitoring System}}
      {Developed a river monitoring subsystem for data acquisition and MQTT transmission, implementing task scheduling and robust error handling.}
    \resumeSubItem{\href{https://github.com/aleemont1/esiot-23-24-assignment2/}{Smart Car Washing}}
      {Led backend development for a smart car washing prototype, engineering task APIs, schedulers, and dependency systems.}
    \resumeSubItem{\href{https://github.com/progetto-oop-22-23/OOP22-HOMER}{HOMER}}
      {Designed system architecture and developed energy monitoring features and smart automation for a Java-based smart home simulator.}
  \resumeSubHeadingListEnd

%--------PUBLICATIONS--------
\section{Publications}
\resumeSubHeadingListStart
\item \textbf{Bachelor Thesis} {\href{https://aleemont1.github.io/bachelor-thesis/pdf/tesi.pdf}{"Development and Optimization of a Telemetry System for Rockets – Architecture and Data Transmission using LoRa\textsuperscript{\textcopyright}"}}
\item \textbf{Research Paper (manuscript in preparation)} {Monticelli A., “A Data Segmentation Protocol for LoRa\textsuperscript{\textcopyright} Transmission” expected submission to IEEE, 2025.}
\resumeSubHeadingListEnd

%--------CERTIFICATES--------
\section{Certificates}
\resumeSubHeadingListStart
    \item{
        \textbf{Cisco Networking Academy}
        {
            \resumeSubHeadingListStart
                \item{\href{https://github.com/aleemont1/curriculum-vitae/blob/main/certificates/PYTHON-2020_certificate.pdf}{PCAP - Programming Essentials in Python}}
                \item{\href{https://github.com/aleemont1/curriculum-vitae/blob/main/certificates/IOT-2018_certificate.pdf}{Introduction to the Internet of Things}}
                \item{\href{https://github.com/aleemont1/curriculum-vitae/blob/main/certificates/GetConnected-2017_certificate.pdf}{Get Connected}}
            \resumeSubHeadingListEnd
        }
    }
    \item{
        \textbf{English}
        {
            \resumeSubHeadingListStart
                \item{\href{https://github.com/aleemont1/curriculum-vitae/blob/main/certificates/English_C1.pdf}{C1 Level Certificate}}
            \resumeSubHeadingListEnd
        }
    }
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
